---
title: "The Road to Chicken Dinner: An analysis of PUBG gameplay statistics"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r}
set.seed(0)
setwd("<Current Working directory of the project>")
```

```{r}
data <- read.csv("Datasets/training/filtered_training.csv", header = TRUE)
test_data <- read.csv("Datasets/testing/filtered_linear_regression_testing.csv", header = TRUE)
```


\textbf{Multiple Linear Regression with all the predictor variables}
```{r}
model = lm(winPlacePerc ~ ., data= data)
summary(model)
```

\textbf{Multiple Linear Regression: w/o KillPoints attributes}
```{r}
model = lm(winPlacePerc ~ . - killPoints, data= data)
summary(model)
```

\textbf{Backward Elimination}
```{r}
model_bwd = lm(winPlacePerc ~ . - killPoints - vehicleDestroys - roadKills - headshotKills , data= data)
summary(model_bwd)
```

```{r}
preds = predict(model_bwd, newdata = test_data)
plot(preds~test_data$winPlacePerc , xlab = "Expected winPlacePerc" , ylab ="Predicted winPlacePerc")
print(paste('Mean Square Error:', sum((preds - test_data$winPlacePerc)^2) / length(preds)))
abline(0, 1, col="red", lwd = 2)
```

```{r}
par(mfrow=c(2, 2))
plot(model_bwd)
```


```{r}
print(paste('Mean Square Error:', sum((preds - test_data$winPlacePerc)^2) / length(preds)))
```

```{r}
summary(model_bwd)$coefficients[,c(0,1)]
```

```{r}
p_vals = summary(model_bwd)$coefficients[,4]
tab = cbind(summary(model_bwd)$coefficients[,0], unname(p_vals),p.adjust(unname(p_vals),method = p.adjust.methods, n=length(unname(p_vals))))
colnames(tab) = c("Unadjusted", "Adjusted")
tab
```

\textbf{Forward Elimination}

```{r}
model_fwd = lm(winPlacePerc ~ walkDistance , data=data)
broom::glance(model_fwd)
#summary(model_fwd)
```


```{r}
model_fwd = lm(winPlacePerc ~ walkDistance + killPlace , data=data)
broom::glance(model_fwd)
```

```{r}
model_fwd = lm(winPlacePerc ~ walkDistance + killPlace + boosts , data=data)
broom::glance(model_fwd)
```


```{r}
model_fwd = lm(winPlacePerc ~ walkDistance + killPlace + boosts + weaponsAcquired , data=data)
broom::glance(model_fwd)
```

```{r}
model_fwd = lm(winPlacePerc ~ walkDistance + killPlace + boosts + weaponsAcquired + kills , data=data)
broom::glance(model_fwd)
```

```{r}
model_fwd = lm(winPlacePerc ~ walkDistance + killPlace + boosts + weaponsAcquired + kills + killStreaks , data=data)
broom::glance(model_fwd)
```

```{r}
model_fwd = lm(winPlacePerc ~ walkDistance + killPlace + boosts + weaponsAcquired + kills + killStreaks + rideDistance , data=data)
broom::glance(model_fwd)
```

```{r}
model_fwd = lm(winPlacePerc ~ walkDistance + killPlace + boosts + weaponsAcquired + kills + killStreaks + rideDistance + assists , data=data)
broom::glance(model_fwd)
```

```{r}
model_fwd = lm(winPlacePerc ~ walkDistance + killPlace + boosts + weaponsAcquired + kills + killStreaks + rideDistance + assists + DBNOs , data=data)
broom::glance(model_fwd)
```


```{r}
model_fwd = lm(winPlacePerc ~ walkDistance + killPlace + boosts + weaponsAcquired + kills + killStreaks + rideDistance + assists + DBNOs + revives , data=data)
broom::glance(model_fwd)
```

```{r}
model_fwd = lm(winPlacePerc ~ walkDistance + killPlace + boosts + weaponsAcquired + kills + killStreaks + rideDistance + assists + DBNOs + revives + swimDistance , data=data)
broom::glance(model_fwd)
```

```{r}
model_fwd = lm(winPlacePerc ~ walkDistance + killPlace + boosts + weaponsAcquired + kills + killStreaks + rideDistance + assists + DBNOs + revives + swimDistance + numGroups , data=data)
broom::glance(model_fwd)
```

```{r}
model_fwd = lm(winPlacePerc ~ walkDistance + killPlace + boosts + weaponsAcquired + kills + killStreaks + rideDistance + assists + DBNOs + revives + swimDistance + numGroups + maxPlace , data=data)
broom::glance(model_fwd)
```

```{r}
model_fwd = lm(winPlacePerc ~ walkDistance + killPlace + boosts + weaponsAcquired + kills + killStreaks + rideDistance + assists + DBNOs + revives + swimDistance + numGroups + maxPlace + matchDuration, data=data)
broom::glance(model_fwd)
```

```{r}
model_fwd = lm(winPlacePerc ~ walkDistance + killPlace + boosts + weaponsAcquired + kills + killStreaks + rideDistance + assists + DBNOs + revives + swimDistance + numGroups + maxPlace + matchDuration + kill_category, data=data)
broom::glance(model_fwd)
```

```{r}
model_fwd = lm(winPlacePerc ~ walkDistance + killPlace + boosts + weaponsAcquired + kills + killStreaks + rideDistance + assists + DBNOs + revives + swimDistance + numGroups + maxPlace + matchDuration + kill_category + matchType, data=data)
broom::glance(model_fwd)
```


\textbf{Building models with respect to commute type}
```{r}
model_walk =lm(winPlacePerc ~ walkDistance, data = data)
summary(model_walk)
```

```{r}
model_walk =lm(winPlacePerc ~ swimDistance, data = data)
summary(model_walk)
```

```{r}
model_walk =lm(winPlacePerc ~ rideDistance, data = data)
summary(model_walk)
```

```{r}
data_swim = data[data$swimDistance>0,]
```



\textbf{Trying to figure out the effect of major attributes to the team play by the pair plot graph}

```{r}
data <- read.csv("Datasets/training/filtered_training_10_matches.csv", header = TRUE)
data$matchType = NULL
temp <- data[, c("assists", "kills", "heals", "revives", "teamKills", "walkDistance", "winPlacePerc")]
pairs(temp)
```

\textbf{Trying to find kills vs winPlacePerc:}

```{r}
data <- read.csv("Datasets/training/filtered_training.csv", header = TRUE)
data$kills = factor(data$kills)
data$matchType = factor(data$matchType)
```

```{r}
L = aov(winPlacePerc ~ kills, data = data)
summary(L)
TukeyHSD(L)
```

\textbf{Trying to figure out the impact of team play attribute}

```{r}
data <- read.csv("Datasets/training/filtered_training.csv", header = TRUE)
team_data = data[data$matchType=="duo" | data$matchType=="duo-fpp" | data$matchType=="squad" | data$matchType=="squad-fpp",]
```

```{r}
model_tp = lm(winPlacePerc ~ assists + revives + teamKills + boosts + heals + killPoints + kills + rankPoints, data= team_data)
summary(model_tp)
```


\textbf{Trying to predict matchType with Logistic Regression}

```{r}
data <- read.csv("Datasets/training/filtered_training.csv", header = TRUE)
test_data <- read.csv("Datasets/testing/filtered_logistic_regression_testing.csv", header = TRUE)
data$matchType = factor(data$matchType)


expected_val = factor(test_data$matchType)
test_data$Id = NULL
test_data$groupId = NULL
test_data$matchId = NULL
```

```{r}
library(nnet)
data$matchType <- relevel(data$matchType, ref=1)
model = multinom(matchType~., data=data, maxit=1000)
summary(model)
```

\textbf{Predict the results using the trained Logistic Regression model on the test set}

```{r}
library(caret)
preds <- predict(model, newdata = test_data)
confusionMatrix(data=preds, reference = expected_val)
```

\textbf {Checking the goodness of fit for the Logistic Regression model}
```{r}
library(generalhoslem)
hl <- logitgof(data$matchType, fitted(model), g = 10, ord = FALSE)
hl$observed
hl$observed
```


\textbf{Training the Logistic Regression model only on the three matchType categories by merging the game types based on the camera view}
```{r}
data <- read.csv("Datasets/training/filtered_training_only_3.csv", header = TRUE)
test_data <- read.csv("Datasets/testing/filtered_logistic_regression_testing_only_3.csv", header = TRUE)
data$matchType = factor(data$matchType)


expected_val = factor(test_data$matchType)
test_data$Id = NULL
test_data$groupId = NULL
test_data$matchId = NULL
```


```{r}
library(nnet)
data$matchType <- relevel(data$matchType, ref=1)
model = multinom(matchType~., data=data, maxit=1000)
summary(model)
```

```{r}
library(caret)
preds <- predict(model, newdata = test_data)
confusionMatrix(data=preds, reference = expected_val)
```

```{r}
library(generalhoslem)
logitgof(data$matchType, fitted(model), g = 10, ord = FALSE)
```